### 2008-12-20 talk/ecoop2009/benchmarks.tex
some minore changes

When doing plain interpretation, we need to create and destroy three temporary
objects at each iteration.  By contrast, the code generated by the JIT does
much better.  At the first iteration, the classes of the two operands of the
multiplication are promoted; then, the JIT compiler knows that both are
integers, so it can inline the code to compute the result.  Moreover, it can
\emph{virtualize} (see section \ref{sec:virtuals} all the temporary objects, because they never escape from
the inner loop.  The same remarks apply to the other two operations inside
the loop.

@@

However, our generated JIT does not compile the whole function at
once. Instead, it compiles and executes code chunk by chunk, waiting until it
knows enough informations to generate highly efficient code.  In particualr,
at the time it emits the code for the inner loop it exactly knows the
type of \lstinline{obj}, thus it can remove the overhead of dynamic dispatch
and inline the method call.  Moreover, since \lstinline{obj} never escapes the
function, it is \emph{virtualized} and its field \lstinline{value} is stored
as a local variable.  As a result, the generated code results in a simple loop
doing additions in-place.

>>>>

When doing plain interpretation, we need to create and destroy three temporary
objects at each iteration.  By contrast, the code generated by the JIT does
much better.  At the first iteration, the classes of the two operands of the
multiplication are promoted; then, the JIT compiler knows that both are
integers, so it can inline the code to compute the result.  Moreover, it can
\emph{virtualize} (see Section \ref{sec:virtuals}) all the temporary objects, because they never escape from
the inner loop.  The same remarks apply to the other two operations inside
the loop.

@@

As already discussed, our generated JIT does not compile the whole function at
once. Instead, it compiles and executes code chunk by chunk, waiting until it
knows enough informations to generate highly efficient code.  In particualr,
at the time it emits the code for the inner loop it exactly knows the
type of \lstinline{obj}, thus it can remove the overhead of dynamic dispatch
and inline the method call.  Moreover, since \lstinline{obj} never escapes the
function, it is \emph{virtualized} and its field \lstinline{value} is stored
as a local variable.  As a result, the generated code results in a simple loop
doing additions in-place.
